%%\documentclass[main]{subfiles}
\textbf{Funding:  }

This work was supported by the BC Cancer Foundation, Terry Fox Research Institute Grant 1082, CCSRI Grant 705617, CIHR Grant FDN-148429 and Stand Up To Cancer Canada/Entertainment Industry Foundation Grant SU2C-AACR-DT-18-15. S.A. is supported by a Canada Research Chair in Molecular Oncology.

\textbf{Author Contributions:  }

T.M. and S.A. designed the overall study and wrote the manuscript. T.M. and C.S. conducted the genetic screens. T.M. analyzed the screen data. T.M., C.S., J.B. performed CGA. T.M., J.B., S.B., performed dose response experiments. H.X. performed immunofluorescence assays for RNF168, FK2, DDR foci. T.M., J.B., S.B. carried out Western blot experiments. T.M., J.B., performed K63-Super-UIM experiments. S.M. performed statistical analysis for CGA and chromatin Western blots. All authors contributed to the writing of the manuscript.    

\textbf{Acknowledgements:  }

We acknowledge Niels Mailand for U2OS cells with K63-Super UIM, Chunaram Choudhary for UBE2N-null HCT116 cells, Daniel Durocher for advice regarding DDR-associated ubiquitination, Esther Kong, Manisha Sarkaria and Almas Khan for help with sub-cloning, Western blots and cell cultures, and BCCRC Flow Cytometry Core especially Wenbo Xu. We thank Shankar Balsubramanian and Marco di Antonio for the gift of bg4 antibody and advice on G4 in vivo detection.

\textbf{Competing interests:  }

S.A. is a founder and shareholder of Contextual Genomics Inc. S.A. is a scientific advisor to Repare Therapeutics and Sangamo Pharmaceuticals. The other authors have no competing interests.

